\documentclass{beamer}
\usetheme{metropolis}

\title{The Greebling}
\subtitle{Scaling Neural-Data Vaults and AI Urbanization in the Bitsmasher Network}
\author{Franklin}
\institute{bitsmasher.net}
\date{April 10, 2026}

\begin{document}
	
	\begin{frame}
		\titlepage
	\end{frame}
	
	\begin{frame}{Abstract}
		Infrastructure expansion within the Skynet AI Testing Field necessitates a transition from legacy flat-file storage to high-density SQL architectures. This session details the technical recovery and scaling of the blowfish node, focusing on the 274GB filesystem exhaustion event, OpenBSD disk re-initialization, and the deployment of the Hub 07 Neural-Data Vault to support the NPUSpatialEngine and T2BM pipeline.
	\end{frame}
	
	\begin{frame}{The 274GB Log Bloat Crisis}
		\begin{itemize}
			\item \textbf{Detection:} Filesystem exhaustion on the /home partition of the blowfish database host.
			\item \textbf{Root Cause:} Rapid expansion of \texttt{mysqld.log} reaching 255 GiB, indicative of service-level error loops.
			\item \textbf{Emergency Response:} Truncation of the log file and implementation of \texttt{newsyslog} rotation policies using the \texttt{rcctl restart mysqld} directive.
		\end{itemize}
	\end{frame}
	
	\begin{frame}{Storage Node Re-Initialization}
		\begin{itemize}
			\item \textbf{Hardware:} Integration of Western Digital 2.8TB My Passport and 1TB Black drives.
			\item \textbf{Filesystem:} Utilization of GUID Partition Table (GPT) and OpenBSD Fast File System (FFS).
			\item \textbf{Optimization:} Alignment for 4096-byte sectors and establishing permanent mounts via DUID in \texttt{/etc/fstab} with \texttt{nodev} and \texttt{nosuid} security flags.
		\end{itemize}
	\end{frame}
	
	\begin{frame}{The Neural-Data Vault (Hub 07)}
		\begin{itemize}
			\item \textbf{Database Migration:} Relocating the MariaDB \texttt{datadir} to the 1TB expansion volume to offload BlueMap SQL tiles.
			\item \textbf{Schema Design:} Deployment of the \texttt{skynet\_vault} database and \texttt{build\_history} table.
			\item \textbf{Telemetry Tracking:} Implementation of the \texttt{ai\_hardware} field to audit inferences from the Hailo-8L NPU and Google Edge TPU.
		\end{itemize}
	\end{frame}
	
	\begin{frame}{Spatial Inference and Density Logic}
		\begin{itemize}
			\item \textbf{NPUSpatialEngine:} Simulating neural signal spread using 10x10 block cells.
			\item \textbf{Collision Detection:} Utilizing SQL-backed build history to prevent structural overlaps in the Testing Field.
			\item \textbf{Vector Selection:} NPU Density Logic for optimal site selection based on 'cluster' or 'void' preferences.
		\end{itemize}
	\end{frame}
	
	\begin{frame}{NFS Cluster Interconnectivity}
		\begin{itemize}
			\item \textbf{Transport:} Configuring NFSv3 over TCP (\texttt{-3, -T}) for stability.
			\item \textbf{Troubleshooting:} Resolving \texttt{rpc.mountd} authentication failures and \texttt{unmatched host} errors on the chonk node.
			\item \textbf{Access Control:} Transitioning to \texttt{no\_root\_squash} to ensure consistent ownership for the \texttt{\_mysql} user across the cluster.
		\end{itemize}
	\end{frame}
	
	\begin{frame}{BlueMap and High-Resolution SQL Storage}
		\begin{itemize}
			\item \textbf{Transition:} Moving from legacy \texttt{storage: "file"} to \texttt{storage: "sql"} for the dreamland (overworld) map.
			\item \textbf{Infrastructure Impact:} Managing high-volume SQL writes generated by the hires-layer and architectural telemetry.
			\item \textbf{Persistence:} Ensuring the 20 TPS performance ceiling is maintained during concurrent re-render operations.
		\end{itemize}
	\end{frame}
	
	\begin{frame}{Future Directions: Urbanizing the Testing Field}
		\begin{itemize}
			\item \textbf{T2BM Pipeline:} Text to Building in Minecraft via Large Language Models.
			\item \textbf{Deep-Rail Integration:} Expanding the transit network from Hub 01 through Hub 07.
			\item \textbf{Ledger Synchronization:} Continuous updates to the GitHub technical ledger to secure infrastructure state.
		\end{itemize}
	\end{frame}
	
\end{document}