\chapter{Schematic Standards \& Voxel Generation}

This chapter formalizes the architectural, stylistic, and structural technical standards for Minecraft schematics within the bitsmasher.net network, optimized specifically for the \textbf{v5 Industrial} era. 

\section{Project History \& Voxelization Evolution}
The bitsmasher.net cluster has evolved through three distinct architectural epochs, shifting from basic gameplay containers to distributed, hardware-accelerated spatial voxelization:

\begin{description}
    \item[The Legacy Era (2012--2020):] Characterized by manual constructions centered around the legacy Train Station. Navigation relied on armor-stand metadata tags, and administrative configurations were maintained via legacy FTB Ranks. 
    \item[The Mycelial Era (2020--2025):] Introduced early automated procedural generation. The aesthetic prioritized organic, mycelial growth networks. However, the lack of spatial safety checks resulted in silent deployment overlaps and frequent chunk-boundary corruption.
    \item[The v5 Industrial Voxel Era (2026--Present):] Decommissioned organic ``Void-Tech'' logic in favor of high-density industrial greebling. Spatial math is offloaded to the local NVIDIA Jetson cluster (Edge-J) and validated via Skynet's Hailo-8L NPU before injection, preserving a constant 20.0 TPS target.
\end{description}

\section{v5 Industrial Aesthetic Specifications}
Transitioning away from legacy biomorphic models, the v5 standard mandates highly structural, mechanically expressive block profiles.

\subsection{Official Material Palette}
All generative building algorithms must resolve abstract voxel requests using the following structural palette:
\begin{itemize}
    \item \textbf{Primary Support Columns:} \texttt{minecraft:purpur\_pillar} (configured as 3$\times$3 fluted cores).
    \item \textbf{Structural Girders:} \texttt{minecraft:dark\_prismarine} (simulating grid-iron assemblies).
    \item \textbf{Industrial Luminance:} \texttt{minecraft:pearlescent\_froglight} (placed strictly at major structural intersections).
    \item \textbf{Temporal Detail Accents:} \texttt{minecraft:waxed\_copper\_block} and its oxidization variants.
    \item \textbf{Foundations \& Retaining Walls:} \texttt{minecraft:polished\_deepslate\_bricks} and \texttt{minecraft:polished\_andesite}.
\end{itemize}

\subsection{Rigorous Design Laws}
To guarantee depth, shadows, and parallax under live rendering engines (such as BlueMap), generative modules enforce three strict rules:
\begin{enumerate}
    \item \textbf{Minimum Bounding Envelope:} Procedural generators must target a minimum bounding box of 20$\times$15$\times$25 blocks. Anything smaller is rejected by the staging database.
    \item \textbf{The Rule of Three:} Flat vertical walls are prohibited. Every exposed structural surface must contain three distinct topological depth steps:
    \begin{equation}
        \text{Surface Depth} = \mathbf{D}_{\text{Base Layer}} \cup \mathbf{D}_{\text{Structural Column}} \cup \mathbf{D}_{\text{Accent Girder}}
    \end{equation}
    \item \textbf{Fluted Pillar Architecture:} Support columns must utilize a 3$\times$3 horizontal footprint. Vertical pillar cores are surrounded by oriented, reversed stairs to create recessed shadowing effects.
\end{enumerate}

\section{The Emerald Mirror Pipeline}
To modify the world state without locking the primary tick thread on Chonk, the cluster orchestrates a four-stage distributed transaction loop:

\begin{equation}
    \text{Inference (Stargate)} \rightarrow \text{Refinement (Jetson Cluster)} \rightarrow \text{Validation (Skynet NPU)} \rightarrow \text{Injection (Chonk RCON)}
\end{equation}

\begin{enumerate}
    \item \textbf{Inference:} Stargate queries Ollama/Vertex AI with a localized spatial snapshot JSON. The model outputs a high-level creative instruction set.
    \item \textbf{Refinement:} Abstract instructions are pushed via SSH/SCP to the CUDA-accelerated Jetson cluster (\texttt{Edge-J01} through \texttt{Edge-J04}). Parallel kernels calculate voxel translations and write the target coordinates into binary format.
    \item \textbf{Validation:} Skynet pulls the generated \texttt{.schem} file into memory, runs metadata integrity scripts, and cross-references its boundaries against protected coordinates using the Hailo-8L NPU.\@
    \item \textbf{Injection:} Stargate transmits the verified changes to the live Paper console via RCON, utilizing asynchronous command throttling to maintain performance.
\end{enumerate}

\section{Metadata Structures \& Schematic Classifications}
To prevent generation algorithms from wiping out player-constructed infrastructure, schematics are divided into two classifications.

\subsection{Classification Rules}
\begin{itemize}
    \item \textbf{Foundation Schematics:} Massive, solid skeletal ``Anchors'' containing permanent structural blocks. These represent the primary base layouts.
    \item \textbf{Delta Schematics:} High-density aesthetic overlays (greebles) containing a high proportion of \texttt{minecraft:air} blocks. These ``wrap'' around existing foundations dynamically.
\end{itemize}

\subsection{Mandatory JSON Payload Schema}
Every schematic transit must contain a companion metadata file. If this block fails validation, the downstream deployment queue on Chonk drops the request immediately:

\begin{lstlisting}[style=bashstyle, caption={Mandatory Schematic Meta Payload}]
{
  "build_id": "industrial_refinery_01",
  "schematic_type": "Foundation",
  "spatial_data": {
    "origin": {
      "x": -1024,
      "y": 63,
      "z": 1280
    },
    "dimensions": {
      "width": 20,
      "height": 15,
      "length": 25
    }
  }
}
\end{lstlisting}